---
title: "First assignment"
author: "Maya"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Summarizing the first assignment in the course

In this assignment I created the R project "HomeAssignment"
And also imported an csv file with meteorological data.

I than created an R fuction called "TD_calc.R"
which calculated the dew point temperature vased on temperature and humidty data.

I than read the data from the meteo data file and, used the fuction to calculate the TD and plot the new information.


```{r TD_calc, include=TRUE}
# simple function to read, analyze and plot

# First we read a set of meteorological observations.
# The data file is constructed of a date, hour (24 observation per day, 3 days), temperature and humidity
source('~/R/HomeAssignment/simple.R')
meteo = read.csv('meteo data.csv',header=T)

# now we can calculate it for the whole set of data
output = TD_calc(hum=meteo$hum, temp=meteo$temp)

# and than plot
plot(output, col = "blue", main = "Dew point temperature calculated for all times", xlab = "time", ylab = "Dew point Temp [C]")
```

Now I also documented the function to create a help file.